Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-11 paper/paper.tex
change s in fig5 and images.
closures.
Updated proof of correctness

A few observations: First observe that the transitions  which involving dereferencing and can lead to \bang are those which have a $H(\rho(x))$ term in their premise for some variable $x$.

>>>>

A few observations: First observe that the transitions which involving
dereferencing and can lead to \bang are those which have a
$H(...)$ term in the transition rule. 
Of these most of the terms are of the form $H(\rho(x))$ which involve a root variable. They start from a root variable.
There is exactly once occurance of $H(l)$ which means a derefencing from a heap location.

In both the cases we show that the dereferences cannot lead to a bang state in a function call less program.

For this we need the following lemma,
1.Consider a let-defined variable $x \leftarrow...$ in . If there is an evaluation path in which the definition is followed by a use i.e an occurrence of (car x) (cdr x) (+ x y) if x & return x, then the demand on $x$ is non-null. 
2. Consider a let definition of the form $z->pi1:(cons x y) in ...$, then the demand on $(\cons\ x\ y)$ includes $0\alpha$ for some $\alpha$ if there is an evaluation path in which there is an occurrence of pi2: (car x) pi2 follows pi1.
